{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-08-30 ident_manu.Rnw
identifiability tables for all state variables are done

% ident all states
<<identdo, eval = F, cache = F>>=
data(tocal_all)

@@

labs <- parcats2(as_df = T) %>% 
    rename(Parameter = shrt) %>% 
    select(Parameter, lngs)

# format tocal_all for identifiability table
# add long parameter name
# get parameter combos with coll < 15 + 1
# format error and coll with scinot
# format category label so no duplicates
totab <- tocal_all$top_all %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>%
  mutate(Parameter = as.character(Parameter)) %>% 
  left_join(., labs, by = 'Parameter') %>% 
  mutate(
    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
    lngs = gsub('_', '', lngs), 
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  split(., .$L1) %>% 
  lapply(function(x){

    sel <- which(x$coll < 15)
    x <- x[sel, ] %>% 
    # x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .) %>%
  mutate(
    error = sapply(error, scinot),
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
    ) %>%
  group_by(stts) %>% 
  nest %>% 
  unnest %>% 
  select(stts, lngs, Parameter, Rank, error, coll) %>% 
  rename(
    Description = lngs, 
    L1 = error
  ) %>% 
  mutate(
    stts = as.character(stts),
    Description = paste0('\\footnotesize{', Description, '}'),
    Parameter = paste0('\\footnotesize{', Parameter, '}')
    ) %>% 
  arrange(stts)

identall1 <- filter(totab, stts %in% 'Dissolved Oxygen')

# final table formatting
descrip <- as.character(identall1$Description)
identall1 <- identall1[,-c(1, 2)]
cap_val<- 'Parameter identifiability for dissolved oxygen.  Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.  Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')

latex( 
  identall1,
  file = '',
  rowlabel = 'Parameter description',
  caption = cap_val,
  caption.loc = 'top',
  size = 'normalsize',
  label = 'tab:identall1',
  rowname = descrip,
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@

% ident all states
<<identall, eval = F, cache = F>>=
data(tocal_all)

@@

labs <- parcats2(as_df = T) %>% 
    rename(Parameter = shrt) %>% 
    select(Parameter, lngs)

# format tocal_all for identifiability table
# add long parameter name
# get parameter combos with coll < 15 + 1
# format error and coll with scinot
# format category label so no duplicates
totab <- lapply(tocal_all, function(x) x$top) %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>% 
  mutate(Parameter = as.character(Parameter)) %>% 
  left_join(., labs, by = 'Parameter') %>% 
  mutate(
    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
    lngs = gsub('_', '', lngs), 
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  split(., .$L1) %>% 
  lapply(function(x){

    sel <- which(x$coll < 15)
    x <- x[sel, ] %>% 
    # x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .) %>%
  mutate(
    error = sapply(error, scinot),
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
    ) %>%
  group_by(stts) %>% 
  nest %>% 
  unnest %>% 
  select(stts, lngs, Parameter, Rank, error, coll) %>% 
  rename(
    Description = lngs, 
    L1 = error
  ) %>% 
  mutate(
    stts = as.character(stts),
    Description = paste0('\\scriptsize{', Description, '}'),
    Parameter = paste0('\\scriptsize{', Parameter, '}')
    ) %>% 
  arrange(stts)

identall2 <- filter(totab, !stts %in% 'Dissolved Oxygen')

# final table formatting
stts <- identall2$stts
descrip <- as.character(identall2$Description)
identall2 <- identall2[,-c(1, 2)]
cap_val<- 'Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.  Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.  Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')

latex( 
  identall2,
  file = '',
  rowlabel = 'State variable, parameter description',
  caption = cap_val,
  caption.loc = 'top',
  size = 'footnotesize',
  label = 'tab:identall2',
  rgroup = unique(as.character(stts)),
  n.rgroup = as.numeric(table(as.character(stts))),
  rowname = descrip,
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@
\clearpage

@@

% phosphatesensitivity all categories
<<po4sens, eval = T, cache = F>>=
senstab(out_var = 'PO4', tablab = 'po4sens', captxt = 'phosphate', digits = 2, pow = 2, tabsize = 'footnotesize')
@

>>>>

% first heuristic, all states
<<heurist1, eval = T, cache = F>>=
data(tocal_all)

# factor levels
cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
cats_lab <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))

# format tocal_all for identifiability table
totab <- lapply(tocal_all, function(x) x$cat) %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>%
  mutate(Parameter = as.character(Parameter)) %>%
  mutate(
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  split(., .$L1) %>% 
  lapply(function(x){

    sel <- which(x$coll < 15)
    x <- x[sel, ] %>%

    # x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .) %>%
  mutate(
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank)
    ) %>%
  group_by(stts) %>% 
  nest %>% 
  unnest %>% 
  select(stts, Category, Parameter, Rank, coll) %>%
  mutate(
    stts = as.character(stts),
    Parameter = paste0('\\footnotesize{', Parameter, '}')
    ) %>% 
  spread(stts, coll, fill = '-') %>% 
  group_by(Parameter) %>% 
  arrange(Category, Rank)

# final table formatting
parms <- totab$Parameter
cats <- as.character(totab$Category)
cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) by category for relevant state variables.  Selections followed the first heuristic where parameters were selected within categories from most to least sensitive until $\\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable.'
colnms <- c('Rank', 'Ammonium', 'Chl-\\textit{a}', 'O$_2$', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')

latex( 
  totab[, -c(1, 2)],
  file = '',
  rowlabel = 'Parameter',
  caption = cap_val,
  caption.loc = 'top',
  size = 'footnotesize',
  label = 'tab:heurist1',
  rowname = parms,
  rgroup = unique(cats),
  n.rgroup = as.numeric(table(cats)),
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@

% second heuristic, all states
<<heurist2, eval = T, cache = F>>=
data(tocal_all)

@@

# format tocal_all for identifiability table
totab <- lapply(tocal_all, function(x) x$top) %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>%
  mutate(Parameter = as.character(Parameter)) %>% 
  mutate(
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  filter(coll < 15) %>% 
  mutate(
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
    ) %>%
  select(stts, Selected, Parameter, Rank, coll) %>%
  mutate(
    stts = as.character(stts),
    Parameter = paste0('\\footnotesize{', Parameter, '}')
    ) %>% 
  arrange(stts, Selected)

# final table formatting
stts <- as.character(totab$stts)
sels <- totab$Selected
cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \\cref{fig:heurist_stts} for a graphical illustration.'
colnms <- c('Parameter', 'Rank', '$\\gamma$')

latex( 
  totab[, -c(1, 2)],
  file = '',
  rowlabel = 'Selections by state variable',
  caption = cap_val,
  caption.loc = 'top',
  size = 'footnotesize',
  label = 'tab:heurist2',
  rowname = sels,
  rgroup = unique(stts),
  n.rgroup = as.numeric(table(stts)),
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@

% third heuristic, all states
<<heurist3, eval = T, cache = F>>=
data(tocal_all)

@@

# format tocal_all for identifiability table
totab <- lapply(tocal_all, function(x) x$cattop) %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>%
  mutate(Parameter = as.character(Parameter)) %>% 
  mutate(
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  filter(coll < 15) %>% 
  mutate(
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
    ) %>%
  select(stts, Selected, Parameter, Rank, coll) %>%
  mutate(
    stts = as.character(stts),
    Parameter = paste0('\\footnotesize{', Parameter, '}')
    ) %>% 
  arrange(stts, Selected)

# final table formatting
stts <- as.character(totab$stts)
sels <- totab$Selected
cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) for relevant state variables.  Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
colnms <- c('Parameter', 'Rank', '$\\gamma$')

latex( 
  totab[, -c(1, 2)],
  file = '',
  rowlabel = 'Selections by state variable',
  caption = cap_val,
  caption.loc = 'top',
  size = 'footnotesize',
  label = 'tab:heurist3',
  rowname = sels,
  rgroup = unique(stts),
  n.rgroup = as.numeric(table(stts)),
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@

\clearpage

@@

% phosphate sensitivity all categories
<<po4sens, eval = T, cache = F>>=
senstab(out_var = 'PO4', tablab = 'po4sens', captxt = 'phosphate', digits = 2, pow = 2, tabsize = 'footnotesize')
@

### 2016-08-30 ident_manu.tex
identifiability tables for all state variables are done

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Aug 24 11:58:31 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% ident all states

% ident all states

@@

% phosphatesensitivity all categories

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Aug 30 11:59:58 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% first heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) by category for relevant state variables.  Selections followed the first heuristic where parameters were selected within categories from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable.\label{tab:heurist1}} 
\begin{tabular}{llllllllll}
\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Ammonium}&\multicolumn{1}{c}{Chl-\textit{a}}&\multicolumn{1}{c}{O$_2$}&\multicolumn{1}{c}{Irradiance}&\multicolumn{1}{c}{Nitrate}&\multicolumn{1}{c}{OM1}&\multicolumn{1}{c}{OM2}&\multicolumn{1}{c}{Phosphate}\tabularnewline
{Optics}&&&&&&&&&\tabularnewline
~~\footnotesize{\textit{astar490}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{astar490}}&$2$&$8.54$&$10.83$&-&-&-&$9.19$&$7.33$&-\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$2$&-&-&$3.86$&$1.43$&-&-&-&$3.63$\tabularnewline
~~\footnotesize{\textit{astarOMZ}}&$3$&-&$13.7$&$3.93$&$3.78$&-&$13.31$&$13.12$&$3.73$\tabularnewline
{Organic Matter}&&&&&&&&&\tabularnewline
~~\footnotesize{\textit{KG1}}&$1$&-&-&-&-&-&$1$&-&$1$\tabularnewline
~~\footnotesize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNH4}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$1$&-&-&$1$&-&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{KG1}}&$2$&-&$3.42$&$1.12$&$1.43$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$6.03$\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.9$&$1.73$&-\tabularnewline
~~\footnotesize{\textit{nitmax}}&$2$&$14.51$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$3$&-&-&$5.31$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$3$&$14.51$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KO2}}&$3$&-&-&-&$6.37$&-&$6.17$&$4.98$&-\tabularnewline
{Phytoplankton}&&&&&&&&&\tabularnewline
~~\footnotesize{\textit{alpha}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$1$&-&-&$1$&$1$&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{QminP}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
~~\footnotesize{\textit{alpha}}&$2$&-&-&$1.66$&$1.36$&$4.98$&-&-&-\tabularnewline
~~\footnotesize{\textit{mA}}&$2$&-&-&-&-&-&-&-&$1.24$\tabularnewline
~~\footnotesize{\textit{umax}}&$2$&$8.51$&$4.64$&-&-&-&$6.1$&$5.36$&-\tabularnewline
~~\footnotesize{\textit{alpha}}&$3$&-&-&-&-&-&-&-&$4.73$\tabularnewline
~~\footnotesize{\textit{mA}}&$3$&$9.18$&$5.26$&$7.56$&$2.7$&-&$7.13$&$6.72$&-\tabularnewline
~~\footnotesize{\textit{respb}}&$4$&$13.74$&$9.62$&-&-&-&$13.32$&$14.3$&-\tabularnewline
~~\footnotesize{\textit{vmaxP}}&$4$&-&-&-&-&-&-&-&$6.18$\tabularnewline
~~\footnotesize{\textit{Qc}}&$5$&-&$13.06$&-&-&-&$13.35$&$14.39$&-\tabularnewline
{Zooplankton}&&&&&&&&&\tabularnewline
~~\footnotesize{\textit{ZQc}}&$1$&-&$1$&$1$&$1$&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{ZQn}}&$1$&$1$&-&-&-&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{ZQp}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
~~\footnotesize{\textit{Zm}}&$2$&-&-&-&-&-&$2.76$&-&-\tabularnewline
~~\footnotesize{\textit{Zrespb}}&$2$&-&$5.46$&-&$5.88$&-&-&-&$1.66$\tabularnewline
~~\footnotesize{\textit{Zm}}&$3$&-&$14.16$&-&-&-&-&-&$4.21$\tabularnewline
~~\footnotesize{\textit{ZQp}}&$3$&-&-&-&-&-&$2.76$&-&-\tabularnewline
~~\footnotesize{\textit{ZQc}}&$4$&-&-&-&-&-&-&-&$5.23$\tabularnewline
~~\footnotesize{\textit{ZQp}}&$4$&-&$14.2$&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Zrespb}}&$4$&-&-&-&-&-&$12.49$&-&-\tabularnewline
~~\footnotesize{\textit{ZQn}}&$5$&-&-&-&-&-&$13.59$&-&-\tabularnewline

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\footnotesize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{Ammonium}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$8.51$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$9.18$\tabularnewline
~~4&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$11.35$\tabularnewline
\hline
{Chlorophyll}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$4.64$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$5.26$\tabularnewline
~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$9.62$\tabularnewline
~~5&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$12.93$\tabularnewline
\hline
{Dissolved Oxygen}&&&\tabularnewline
~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{Irradiance}&&&\tabularnewline
~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
~~3&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$2.5$\tabularnewline
~~4&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$2.92$\tabularnewline
\hline
{Nitrate}&&&\tabularnewline
~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{OM1}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$6.1$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$7.13$\tabularnewline
~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$13.32$\tabularnewline
~~5&\footnotesize{\textit{Qc}}&$5$\textsuperscript{P}&$13.35$\tabularnewline
\hline
{OM2}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$5.36$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$6.72$\tabularnewline
~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$14.3$\tabularnewline
~~5&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$14.9$\tabularnewline
\hline
{Phosphate}&&&\tabularnewline
~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$1.24$\tabularnewline
~~3&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.73$\tabularnewline
~~4&\footnotesize{\textit{vmaxP}}&$4$\textsuperscript{P}&$6.18$\tabularnewline
~~5&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.17$\tabularnewline
\hline
\end{tabular}\end{center}}

% third heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\footnotesize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:heurist3}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{Ammonium}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$1.67$\tabularnewline
~~3&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.96$\tabularnewline
~~4&\footnotesize{\textit{ZQn}}&$1$\textsuperscript{Z}&$3.61$\tabularnewline
~~5&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$4.97$\tabularnewline
\hline
{Chlorophyll}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.36$\tabularnewline
~~3&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$6.39$\tabularnewline
~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$13.97$\tabularnewline
\hline
{Dissolved Oxygen}&&&\tabularnewline
~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{Irradiance}&&&\tabularnewline
~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
~~3&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.97$\tabularnewline
~~4&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$5.14$\tabularnewline
~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$6.62$\tabularnewline
~~6&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$12.85$\tabularnewline
\hline
{Nitrate}&&&\tabularnewline
~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{OM1}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.73$\tabularnewline
~~3&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$2.77$\tabularnewline
~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$6.91$\tabularnewline
~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$6.91$\tabularnewline
~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$13.68$\tabularnewline
\hline
{OM2}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.46$\tabularnewline
~~3&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.53$\tabularnewline
~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$7.69$\tabularnewline
~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$7.87$\tabularnewline
\hline
{Phosphate}&&&\tabularnewline
~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$1.3$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

% phosphate sensitivity all categories
